Run aquaculture model for Atlantic salmon

### 2025-07-30 06_run_atlantic_salmon_model.qmd
Finishing up run script

here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)
```

@@

# Check that the feed will actually work
targets::tar_make(test_reference_feed)
targets::tar_load(test_reference_feed)
test_reference_feed # should be ~1430 g

@@

targets::tar_validate()
# targets::tar_visnetwork(targets_only = T)
# targets::tar_outdated()
targets::tar_make(
  names = "sens_results_spec",
  seconds_meta_append = 120
  )
```

@@

sens_measures <- levels(sens_results$measure)
sens_results_files <- file.path(output_sens_data_path, paste0("sens_results_", sens_measures, ".qs"))
sens_results_figfiles <- file.path(output_sens_data_path, paste0("sens_plot_", sens_measures, ".qs"))
sens_results_figfiles2 <- file.path(output_sens_data_path, paste0("sens_plot_", sens_measures, ".png"))

for (sm in seq_along(sens_measures)) {
  sens_results %>% 
    filter(measure == sens_measures[sm]) %>% 
    qsave(sens_results_files[sm])

  p <- sens_results %>% 
    filter(measure == sens_measures[sm]) %>% 
    ggplot(aes(x = adj_param, y = mean_sens, ymin = mean_sens-sd_sens, ymax = mean_sens+sd_sens)) +
    geom_col(fill = "salmon", alpha = 0.65, colour = "black") +
    geom_errorbar(width = 0.5) +
    coord_flip() +
    theme_classic()
  qsave(p, sens_results_figfiles[sm])
  ggsave(sens_results_figfiles2[sm])
}
```

@@

Note that this also takes a long time - each branch of farmrun takes ~4.5 minutes, and a maximum of ~12 workers can run at a time. The total therefore takes ~17 hours.

@@

targets::tar_validate()
# targets::tar_visnetwork(targets_only = T)
# targets::tar_outdated()
targets::tar_make(farm_results, seconds_meta_append = 90)
meta <- targets::tar_meta() %>% 
  filter(grepl("farm_run", name))
meta$seconds %>% mean()/60
```

```{r}
#| label: farm-run-results

targets::tar_load(cohort_results)
```

>>>>

here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% str_subset("map", negate = T) %>% walk(source)
```

@@

# Check that the feed will actually work
targets::tar_make(test_reference_feed)
targets::tar_load(test_reference_feed)
test_reference_feed # should be ~1430 g, or really anything other than 0

@@

targets::tar_validate()
# targets::tar_visnetwork(targets_only = T)
# targets::tar_outdated()
targets::tar_make(
  seconds_meta_append = 120,
  callr_function = NULL
  )
```

@@

qs::qsave(sens_results, file.path(output_sens_data_path, paste0("sens_results_all.qs")))

sens_measures <- levels(sens_results$measure)
sens_results_figfiles <- file.path(output_sens_data_path, paste0("sens_plot_", sens_measures, ".qs"))
sens_results_figfiles2 <- file.path(output_sens_data_path, paste0("sens_plot_", sens_measures, ".png"))

for (sm in seq_along(sens_measures)) {
  p <- sens_results %>% 
    filter(measure == sens_measures[sm]) %>% 
    ggplot(aes(x = adj_param, y = mean_sens, ymin = mean_sens-sd_sens, ymax = mean_sens+sd_sens)) +
    geom_col(fill = "salmon", alpha = 0.65, colour = "black") +
    geom_errorbar(width = 0.5) +
    coord_flip() +
    theme_classic()
  qsave(p, sens_results_figfiles[sm])
  ggsave(sens_results_figfiles2[sm])
}
```

@@

Note that this takes a long time - each branch of farmrun takes ~5.3 minutes, and a maximum of ~12 workers can run at a time. The total therefore takes ~17 hours.

@@

targets::tar_validate()
targets::tar_outdated()
targets::tar_prune()

# Pre-run to reduce load
targets::tar_make(
  names = !c("farm_run", "cohort_results", "biomass_produced", "farm_results"), 
  seconds_meta_append = 90,
  callr_function = NULL
)

# Run results
targets::tar_make(
  names = c("farm_run", "cohort_results", "biomass_produced", "farm_results"), 
  seconds_meta_append = 90,
  shortcut = T,
  callr_function = NULL
)

meta <- targets::tar_meta() %>% 
  filter(grepl("farm_run", name))
meta$seconds %>% mean()/60 # average minutes per target
```

Load objects from the targets pipeline and save them as .qs files, which are much quicker to load down the line. This takes a few minutes to gather all the targets.

```{r}
#| label: all-farms-cohorts-results

targets::tar_load(stat_names)
targets::tar_load(farm_IDs)
targets::tar_load(feed_names)

print("Loading farm results...")
targets::tar_load(farm_results)
for (stat_name in stat_names) {
  farm_results %>% 
      filter(measure == stat_name) %>% 
      qsave(file.path(output_model_farm_path, str_c(stat_name, "_all_farms.qs")))
}
rm(farm_results)

print("Loading cohort results...")
targets::tar_load(cohort_results)
for (stat_name in stat_names) {
  cohort_results %>% 
      filter(measure == stat_name) %>% 
      qsave(file.path(output_model_cohort_path, str_c(stat_name, "_all_farms.qs")))
}
rm(cohort_results)

targets::tar_load(biomass_produced)
qsave(biomass_produced, file.path(output_model_farm_path, str_c("biomass_produced_all_farms.qs")))
```

```{r}

```
